---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/README-",
  out.width = "100%"
)

Sys.setenv(MINION_PATH = "/home/matthew/bin/minion-1.8")
```

# rminion

A simple wrapper around the
[Minion](https://github.com/minion/minion)
constraint solver.

## Installation

### Minion

To install Minion, download the Minion repository. The
Minion executable is found in the `bin/` folder.

### R Package

```{r eval = FALSE}
remotes::install_github("MHenderson/rminion")
```

## Run

Assuming that the Minion repository has been downloaded
and that an environment variable `MINION_PATH` has been
defined which points to the location of the Minion repository,
then we can run one of the benchmark examples like so.

```{r eval = TRUE}
library(rminion)

dgr_path <- file.path(Sys.getenv("MINION_PATH"), "benchmarks/small/donaldgeraldrobert.minion")

minion(dgr_path)
```
